### 2014-06-02 patchy-selection-paper.tex

As our goal here to describe the rough genomic length scale, 
based on the above, we view 
the lineage is simply bouncing around in the patch backward in time and we propose a
simple heurstic to describe the probability of recombination. 
If recombination is on a slower time scale than mixing within the patch,
then the time until the last recombination is the integral of $r (1-p(x)) (1+s(x)/2)$ 
against the stationary distribution (eqn. \ref{eqn:lineagestatdist}).
Within the patch, $p(x) \approx 1$,
so recombination off the $B$ background is unlikely to occur,
and so the rate of recombination depends to a first approximation 
on the proportion of the patch in which $p(x)$ is intermediate,
i.e. were both $B$ and $b$ are present.
This region where $p(x)$ is intermediate has width of order $\sigma/\sqrt{s}$, where $s = \min(s_p,s_m)$.
As we increase the size of a patch, the area on which $p(x)$ is intermediate scales with the perimeter of the patch.
Therefore, the proportion of the time a lineage at stationarity is found in the intermediate regions
multiplied by $p(x)$ in these intermediate regions, where we assume
$p(x) \approx 1/2$. Under these approximations the per generation rate of
recombination of a linked lineage to the b background is, taking in this region, roughly 
\begin{align}
&=
    \begin{cases}
    r \frac{\frac{\sigma}{\sqrt{s}} }{\frac{\sigma}{\sqrt{s}} + A }    \qquad & d=1 \\
   r \frac{\pi  \frac{\sigma}{\sqrt{s}} \left( \frac{\sigma}{\sqrt{s}} +
  \sqrt{\frac{A}{\pi}} \right)}{A+\pi  \frac{\sigma}{\sqrt{s}} \left( \frac{\sigma}{\sqrt{s}} +
  \sqrt{\frac{A}{\pi}} \right) }    \qquad & d=2 \\  
\end{cases}
\label{eqn:rate-rec-in-patch}   %(\sigma/\sqrt{s})A^{-1/d}
\end{align}
\gc{Altered the above.}
We can use this to first of all think about the length of haplotype
associated with the $B$ allele after a given length of time $\tau$,
this could the the time since the sweep within a patch due to a
mutation or migration of a beneficial allele. If the recombination
rate per base is $r_{BP}$ then the length of haplotype associated with
the $B$ allele is
\begin{equation}
\frac{\sqrt{s}}{\sigma A^{-1/d}}\frac{1}{r_{BP}}
\end{equation} 
note that the length of haplotype decays at a rate proportional to the
cline width $\sqrt{s} / \sigma$, as the narrower the cline the less
opportunity for recombination to move our lineage off the $B$
background.

>>>>

As our goal here to describe the rough genomic length scale, 
based on the above, we view 
the lineage is simply bouncing around in the patch backward in time and we propose a
simple heurstic to describe the probability of recombination. 
If recombination is on a slower time scale than mixing within the patch,
then the time until the last recombination is the integral of $r (1-p(x)) (1+s(x)/2)$ 
against the stationary distribution (eqn. \ref{eqn:lineagestatdist}).
Within the patch, $p(x) \approx 1$,
so recombination off the $B$ background is unlikely to occur,
and so the rate of recombination depends to a first approximation 
on the proportion of the patch in which $p(x)$ is intermediate,
i.e. were both $B$ and $b$ are present.
This region where $p(x)$ is intermediate has width of order $\sigma/\sqrt{s}$, where $s = \min(s_p,s_m)$.
As we increase the size of a patch, the area on which $p(x)$ is intermediate scales with the perimeter of the patch.
Therefore, the proportion of the time a lineage at stationarity is found in the intermediate regions
multiplied by $p(x)$ in these intermediate regions, where we assume
$p(x) \approx 1/2$. Under these approximations the per generation rate of
recombination of a linked lineage to the b background is, taking in this region, roughly 
% \begin{equation}
% r (\sigma/\sqrt{s})A^{-1/d} \label{eqn:rate-rec-in-patch}
% \end{equation}
\begin{align}
&=
    \begin{cases}
    r \frac{\frac{\sigma}{\sqrt{s}} }{\frac{\sigma}{\sqrt{s}} + A }    \qquad & d=1 \\
   r \frac{\pi  \frac{\sigma}{\sqrt{s}} \left( \frac{\sigma}{\sqrt{s}} +
  \sqrt{\frac{A}{\pi}} \right)}{A+\pi  \frac{\sigma}{\sqrt{s}} \left( \frac{\sigma}{\sqrt{s}} +
  \sqrt{\frac{A}{\pi}} \right) }    \qquad & d=2 \\  
\end{cases}
\label{eqn:rate-rec-in-patch}   %(\sigma/\sqrt{s})A^{-1/d}
\end{align}
We can use this to first of all think about the length of haplotype
associated with the $B$ allele after a given length of time $\tau$,
this could the the time since the sweep within a patch due to a
mutation or migration of a beneficial allele. If the recombination
rate per base is $r_{BP}$ then the length of haplotype associated with
the $B$ allele is
\begin{equation}
\frac{\sqrt{s}}{\sigma A^{-1/d}}\frac{1}{r_{BP}}
\end{equation} 
note that the length of haplotype decays at a rate proportional to the
cline width $\sqrt{s} / \sigma$, as the narrower the cline the less
opportunity for recombination to move our lineage off the $B$
background.
